Microscopy Data

### 2019-06-26 Microscopy Data.Rmd
ggplot functions added

```{r setup, include=FALSE}

PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
PA01wt<- c('3-26-19','4-18-19')
PA01mut<- c('4-23-19')

Get<- function (sample){
  bugCounts<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/", sample,"/results"),header = TRUE)
  bugCounts<- na.omit(bugCounts)
  bugCounts<-bugCounts %>% mutate(logTranformed = log10(CFU))
  bugCounts$sample<-sample
  return(bugCounts)
}

@@

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}

testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/results/t00_p1.csv"

GetResults<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
return(growthDf)
}

testGetResults<- GetResults("3-13-19")

ReadResultsFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}
```

@@

testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t00_p1.csv"

GetAggregates<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))}}
return(growthDf)
}

testGetResults<- GetResults("3-13-19")

@@

testReadAggregateFile<-ReadAggregateFile(tes)
```
You can also embed plots, for example:

```{r pressure, echo=FALSE}
GetNumber<-function(idx){
  if (idx<10){
    idx = paste0(0,idx)
  }
  return (idx)
}
```

>>>>

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(tidyr)
library(purrr)

PA14wt<- c('3-13-19', '3-19-19', '4-17-19')
PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
PA01wt<- c('3-26-19','4-18-19')
PA01mut<- c('4-23-19')
names3<-c('rep1','rep2','rep3')
names2<-c('rep1','rep2')

@@

```{r thresholds}

testThresholdFile<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/threshold/threshold_p_0.csv"

wtThresholds<-MapThreshold(PA14wt, names3)
mutThresholds<-MapThreshold(PA14mut, names3)
Pa01Thresholds<-MapThreshold(PA01wt, names2)
Pa01mutThresholds<-MapThreshold(PA01mut, 'rep1')

MapThreshold<- function(listSamples, reps){
  mappedData<-map2(listSamples, reps, GetThresholds)
  boundData<-bind_rows(mappedData)
  return(boundData)
  }

GetThresholds<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/threshold')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    growthDf<-rbind(growthDf,ReadThresholdFile(currentPosition, position))}
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

ReadThresholdFile<-function(file, position ){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = row_number()-1)
  return(datos)
}

```{r biomass}

wtResults<-MapResults(PA14wt, names3)
mutResults<-MapResults(PA14mut, names3)
Pa01Results<-MapResults(PA01wt, names2)
Pa01mutResults<-MapResults(PA01mut, 'rep1')

MapResults<- function(listSamples, reps){
  blah <-deparse(substitute(listSamples))
  mappedData<-map2(listSamples, reps, GetResults)
  boundData<-bind_rows(mappedData)
  boundData<-boundData %>% mutate(Strain = blah)
  return(boundData)
  }

GetResults<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/results')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

ReadResultsFile<-function(file, position, timepoint){
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}

@@

wtAggregates<-MapAggregates(PA14wt, names3)
mutAggregates<-MapAggregates(PA14mut, names3)
Pa01Results<-MapAggregates(PA01wt, names2)
Pa01mutResults<-MapAggregates(PA01mut, 'rep1')

MapAggregates<- function(listSamples, reps){
  mappedData<-map2(listSamples, reps, GetAggregates)
  boundData<-bind_rows(mappedData)
  blah <-deparse(substitute(listSamples))
  boundData<-boundData %>% mutate(Strain = blah)#needs to be two lines, it doesnt work if you do it directly
  return(boundData)
  }

GetAggregates<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
      }
  }
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

@@

```
You can also embed plots, for example:

```{r support functions, echo=FALSE}

GetNumber<-function(idx){
  if (idx<10){
    idx = paste0(0,idx)
  }
  return (idx)
}
```
